Title

### 2013-02-07 inc/magnetic_lenses/maglens.tex
a little reorg to start free-space space-charge section
work on short titles for figures (continuing)

Magnetic lenses present some challenges for Ultrafast Electron Microscopy.
First, the beams are likely to be much larger and thus a UEM will need large-aperture lenses.
Second, and more importantly, near a lens crossover (i.e. focus), the charge density can increase rapidly.
This charge density can lead to an unacceptable amount of space-charge interaction (see section \ref{sec:model_results}).

@@

\begin{figure}
  \centering
  \input{polepiece-schematic}
  \caption{
    Side-view schematic of a shielded magnetic lens with a pole-piece.
    The windings (current loops) are contained within the shielding.
    The magnetic field created by these windings is contained inside the shielding except in the gap.
  }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{maglens.jpg}
  \caption{
    Side view of the two custom large-bore magnetic lenses designed and built at UIC, seen installed in the prototype UEM.
    The coils are visible as is high permeability shielding used for the pole-piece.
    The outer (larger) plates and struts are for structural integrity only.
  }
  \label{fig:maglens-pic}
\end{figure}

>>>>

Magnetic lenses present some challenges for Ultrafast Electron Microscopy.
First, the beams are likely to be much larger and thus a UEM will need large-aperture lenses.
Second, and more importantly, near a lens crossover (i.e. focus), the charge density can increase rapidly.
This charge density can lead to an unacceptable amount of space-charge interaction (see section \ref{sec:free_spacecharge}).

@@

\begin{figure}
  \centering
  \input{polepiece-schematic}
  \caption[Side-view schematic of a shielded magnetic lens with a pole-piece]{
    Side-view schematic of a shielded magnetic lens with a pole-piece.
    The windings (current loops) are contained within the shielding.
    The magnetic field created by these windings is contained inside the shielding except in the gap.
  }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{maglens.jpg}
  \caption[Side-view picture of the employed two custom large-bore magnetic lenses]{
    Side-view of the two custom large-bore magnetic lenses designed and built at UIC, seen installed in the prototype UEM.
    The coils are visible as is high permeability shielding used for the pole-piece.
    The outer (larger) plates and struts are for structural integrity only.
  }
  \label{fig:maglens-pic}
\end{figure}

### 2013-02-07 inc/photocathode/este/este.tex
work on short titles for figures (continuing)

\begin{figure}
  \centering
  \input{fig2}
  \caption{
    Measured Fourier plane electron beam size (HWe$^{-1}$M; squares) and electron yield (circles) as a function of the incident $\sim$200fs, 523nm laser pulse energy for the 300nm-thick gold photocathode.
    The electron yield is proportional to the square of laser pulse energy (solid line) and the dependence of the beam size with the laser pulse energy fits that predicted by a zero free parameter electron heating model (solid line; dashed lines represent $\pm$10\% error in the laser spot size).
    A representative raw Fourier plane beam image is also shown.
  }
  \label{fig:gold-emission}
\end{figure}

@@

\begin{figure}
  \centering
  \input{fig3}
  \caption{
    Number of electrons emitted per pulse as a function of the incident 261nm, UV laser pulse energy for GaSb (open squares) and InSb (filled circles): Linear efficiency dependences are shown by the solid lines.
    The laser pulse energy invariance of the Fourier plane electron beam size (HWe$^{-1}$M right axis; open squares) for GaSb and a representative raw Fourier plane beam image is also shown.
  }
  \label{fig:este-semicond}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{fig2}
  \caption[Measured Fourier plane electron beam size and yield vs incident laser pulse energy on gold photocathode]{
    Measured Fourier plane electron beam size (HWe$^{-1}$M; squares) and electron yield (circles) as a function of the incident $\sim$200fs, 523nm laser pulse energy for the 300nm-thick gold photocathode.
    The electron yield is proportional to the square of laser pulse energy (solid line) and the dependence of the beam size with the laser pulse energy fits that predicted by a zero free parameter electron heating model (solid line; dashed lines represent $\pm$10\% error in the laser spot size).
    A representative raw Fourier plane beam image is also shown.
  }
  \label{fig:gold-emission}
\end{figure}

@@

\begin{figure}
  \centering
  \input{fig3}
  \caption[Electron emission vs UV laser pulse energy for GaSb and InSb]{
    Number of electrons emitted per pulse as a function of the incident 261nm, UV laser pulse energy for GaSb (open squares) and InSb (filled circles): Linear efficiency dependences are shown by the solid lines.
    The laser pulse energy invariance of the Fourier plane electron beam size (HWe$^{-1}$M right axis; open squares) for GaSb and a representative raw Fourier plane beam image is also shown.
  }
  \label{fig:este-semicond}
\end{figure}

### 2013-02-07 inc/photocathode/plasmon/plasmon.tex
work on short titles for figures (continuing)

\begin{figure}
  \centering
  \input{grating_schematic}
  \caption{Schematic diagram of a grating coupling geometry for driving a surface plasmon}
  \label{fig:plasmon_schematic}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{damage.png}
  \caption{Damage to commerical gold-on-glass holographic grating.}
  \label{fig:grating-damage}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{HighMagSEM.jpg}
  \caption{
    SEM image of sinusoidal grating on silicon.
    Pattern milled by focused ion beam milling at Argonne National Lab.
    Sample was later coated with 300 nm gold film.
  }
  \label{fig:fib-si-sem}
\end{figure}

@@

\begin{figure}
  \centering
  \input{power_seq}
  \caption{
    Photoemission characteristics of laser-driven plasmons on a one-dimensional periodic gold surface.
    Top: Electron emission strength as a function of incident 523nm femtosecond laser pulse intensity for coherently-driven plasmons (top curve)
      % with parabolic fit to initial dependence (dashed curve)
      and comparative emission from a plane gold surface under the same irradiantion conditions.
    Bottom: Two-dimensional electron momentum distributions for plasmon-assisted emission (A-D) and two-photon field emission from gold (E) at the laser intensities indicated on the top graph.
    The circular aperture visible in B-D is the 6mm-diameter bore of the magnetic focusing lens.
    The orientation of the grating lines of the periodic gold surface with respect to the emission in A-D is parallel to the broadening seen in B-D.
  }
  \label{fig:pape}
\end{figure}

@@

\begin{figure}
  \centering
  \input{rotated}
  \caption{
    Comparison of the colinear (above) and rotated (below) plasmonic excitation geometries.
    This rotation separates the directionality of effects caused by the laser, plasmon field and grating.
    Each vector diagrams (left) is shown next to a representative observed momentum distribution image (right).
    The increased divergence is shown to be rotated by the same $45^{\circ}$ as the grating (the original colinear line is shown dashed); evidence that the grating is the cause of the deleterious effect.
  }
  \label{fig:rotated}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{grating_schematic}
  \caption[Grating coupling geometry for driving a surface plasmon]{Schematic diagram of a grating coupling geometry for driving a surface plasmon}
  \label{fig:plasmon_schematic}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{damage.png}
  \caption{Damage to commerical gold-on-glass holographic grating}
  \label{fig:grating-damage}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{HighMagSEM.jpg}
  \caption[SEM image of sinusoidal grating on silicon]{
    SEM image of sinusoidal grating on silicon.
    Pattern milled by focused ion beam milling at Argonne National Lab.
    Sample was later coated with 300 nm gold film.
  }
  \label{fig:fib-si-sem}
\end{figure}

@@

\begin{figure}
  \centering
  \input{power_seq}
  \caption[Photoemission characteristics of laser-driven plasmons on a one-dimensional periodic gold surface]{
    Photoemission characteristics of laser-driven plasmons on a one-dimensional periodic gold surface.
    Top: Electron emission strength as a function of incident 523nm femtosecond laser pulse intensity for coherently-driven plasmons (top curve)
      % with parabolic fit to initial dependence (dashed curve)
      and comparative emission from a plane gold surface under the same irradiantion conditions.
    Bottom: Two-dimensional electron momentum distributions for plasmon-assisted emission (A-D) and two-photon field emission from gold (E) at the laser intensities indicated on the top graph.
    The circular aperture visible in B-D is the 6mm-diameter bore of the magnetic focusing lens.
    The orientation of the grating lines of the periodic gold surface with respect to the emission in A-D is parallel to the broadening seen in B-D.
  }
  \label{fig:pape}
\end{figure}

@@

\begin{figure}
  \centering
  \input{rotated}
  \caption[Comparison of the colinear and rotated plasmonic excitation geometries]{
    Comparison of the colinear (above) and rotated (below) plasmonic excitation geometries.
    This rotation separates the directionality of effects caused by the laser, plasmon field and grating.
    Each vector diagrams (left) is shown next to a representative observed momentum distribution image (right).
    The increased divergence is shown to be rotated by the same $45^{\circ}$ as the grating (the original colinear line is shown dashed); evidence that the grating is the cause of the deleterious effect.
  }
  \label{fig:rotated}
\end{figure}
